QPLIB: A Library of Quadratic Programming Instances

### 2018-01-24 AnswerToTheReferees.tex

\documentclass[11pt]{article}
\usepackage[american]{babel}
%\usepackage{a4wide,paralist,url,xcolor,xspace}
\usepackage{a4wide,url,xcolor,xspace}
\definecolor{acblue}{rgb}{0,0,1}
\definecolor{acgreen}{rgb}{0,1,0}
\definecolor{acred}{rgb}{1,0,0}
\newcommand{\rep}[1]{{\textcolor{acblue}{#1}}}
%\newcommand{\comm}[1]{{\textcolor{acgreen}{#1}}}
\newcommand{\comm}[1]{}
\newcommand{\todo}[1]{{\textcolor{acred}{#1}}}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{booktabs}
\usepackage{multirow}

@@

\section*{QPLIB: a Library of a Quadratic Programming Instances (MPC-022017-00003)-- Answer to the Referees}

\rep{
 Following the Area Editor suggestions, we 
 performed a deep revision of our manuscript. We carefully took into account all the comments made by the Referees and the Associate Editor.
 [\dots]
 The new submitted document highlights in red the text that has been
added or changed.
In the following, the comments of the Associate Editor and of the Referees are reported, together with our point-by-point replies.
}

\subsection*{Reply to the Associate Editor}

{\it
I have received two reviews for this manuscript, and while there is consensus that the library makes an important contribution, one of the reviewers in particular had significant concerns with the library and the manuscript describing it. The most significant concern, which I share, is that the paper is significantly longer than it needs to be. In particular, I did not see a great need to review the solution methods as is done in Section 2.3. Mentioning the current solvers, and which classes of problems they can solve according to your taxonomy is perhaps useful for a reader's reference. But attempting to describe the algorithms themselves is somewhat futile, as it takes significant space and yet is still an inadequate description. For that, it would be better to simply provide some references for the benefit of readers who are interested in understanding the algorithms in the solvers. 
}

\rep{We agree with the AE that the description of the solution methods goes beyond the scope of the paper. For this reason we have streamlined Section 2.3 which now contains only a quick overview of the solvers and their solution methods. 
%\leo{Togliamo la spiegazione degli algoritmi e sostituiamola con una citazione di un book-tutorial-survey-introduction.}
}

{\it
I also agree with the reviewer's concern that some of the instance classes have only a single instance in them. If I am a researcher designing a method for solving instances in that class, I will be pretty disappointed to find that QPLIB only has a single relevant test instance. 
}

\rep{
We performed an internal call for instances among the members of the committee. 
Thanks to this new research, we gathered $86$ new instances and we added them to the library. The updated division of the instances is as follows:\\
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{6}*{Linear}
          & \multirow{2}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Convex    &   0 +\textcolor{red}{xx}\\[1.2 ex]
           &         & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2 +\textcolor{red}{xx}\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  2  +\textcolor{red}{xx}\\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   12\\[1.2 ex]
\multirow{1}*{Concave (if max)}
          &         & Quadratic &    1 +\textcolor{red}{xx}\\[1.2 ex]
%          & General & Linear    &    \\
%\cmidrule(lr){2-4}
%          & \multirow{1}*{Integer}
%                    & Linear    &   1\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   11\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
\cmidrule(lr){2-4}
          & Integer & Linear    &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total Discrete     &         &           & 251 +\textcolor{red}{xx}\\
%
\bottomrule
\end{tabular}\\\\
%
%
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   13\\[1.2 ex]
                         & Quadratic &   48\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{1}*{Convex (if min)}
                         & Box       &   3 \\[1.2 ex]
\multirow{1}*{or}
                         & Linear    &   11\\[1.2 ex]
                        % & Convex    &    2\\[1.2 ex]
\multirow{1}*{Concave (if max)}
                         & Quadratic &    6\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{3}*{Quadratic}
                         & Linear    &   6\\[1.2 ex]
                         & Convex    &   1\\[1.2 ex]
                         & Quadratic &   28\\[1.2 ex]
\hline
Total Continuous                   &           & 116 +\textcolor{red}{18} \\
%
\bottomrule
\end{tabular}\\
All the new instances 
%%
%\leo{Sono d'accordo, ma come/dove troviamo le istanze supplementari? Sono le categorie con  $<10$ istanze nelle tavole 4 e 5, giusto? Dire che ce ne sono parecchie. 15 categorie su 23 hanno meno di 10 istanze (il numero 10 e` magico perche' le nostre mani hanno dieci dita, ovviamente).} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Variables & Convexity & \#\\
\cmidrule(lr){1-3}
%
 Continuous	& Convex		&  27+\textcolor{red}{yy} \\[1.2 ex]
 Continuous	& Non Convex	&  89+\textcolor{red}{yy} \\[1.2 ex]
 Discrete	& Convex		&  16+\textcolor{red}{63} \\[1.2 ex]
 Discrete	& Non Convex	&  235+\textcolor{red}{5} \\[1.2 ex]
\cmidrule(lr){1-3}
Total		&				& 367+\textcolor{red}{86}\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item I think it would be interesting to mention the Conic library CBLIB \url{http://cblib.zib.de} and its relation to the library described in the manuscript.

\rep{TODO:Fabio and Emiliano}

\item Page 7, line -4. You say that convex means that the feasible region is
convex, but in page 19 you discuss the fact that SOCP problems that have
a convex feasible region could be considered nonconvex. Hence, maybe it
is more accurate to say that what you mean is that the constraint can be
converted to $f (x) \le c$ with $f$ convex by rearranging terms.

\rep{ TODO: Leo 
%\leo{secondo me il secondo commento si riferisce a pagina 19... a pagina 7 riga -4 non trovo niente su SOCP. Pero` sono d'accordo che a pagina 19 l'ultimo paragrafo della sezione 3.1 potrebbe essere migliorato. Cosi` e` un po' criptico. Perche' non inserire un bell'esempio di una forma bilineare nonconvessa (scrivendola esplicitamente come xQx e dando esplicitamente lo spettro di Q con la parte definita negativa) inserita in un vincolo che definisce una regione convessa? E poi io direi che facciamo la scelta di mettere queste istanze come "nonconvesse" perche' dimostrare convessita` in generale e` difficile (a questo proposito, io conosco i risultati del PhD di Amir Ali Ahmadi sulla difficolta` di riconoscere la convessita` in polinomi di grado $>= 4$, ma non ho mai visto una dimostrazione di difficolta` di riconoscere la convessita` della feasible region in vincoli quadratici; spero che qualcuno dei nostri co-autori ne sia al corrente)... Il referee ricorda che riconoscere i casi di forme quadratiche con una negative eigenvalue inserite in un vincolo convesso e` facile e  da` un metodo, di cui sarebbe bene ritrovare il primo caso in cui viene menzionato, oppure darne una breve dimostrazione... io non ne ero a conoscenza (e nemmeno mi viene in mente sui due piedi come dimostrarlo).} 
}

@@

\item Page 17. Doesn't CPLEX support some binary non-convex quadratic
problems.

\rep{ TODO:Fabio and Emiliano
%\leo{rispondiamo al referee che CPLEX e` classificato 'C' (complete) in tavola 2 rispetto a QGC e ricordiamogli che pero` CPLEX non risolve (a mia conoscenza e per il momento) QGQ. Tra l'altro, c'e` a p. 17 una menzione di "Table 2 below", tranne che la table 2 appare above. Diciamo solo "Table 2" senza il below e l'above, dato che la posizione di tavole e figure puo` comunque essere modificata sia da LaTeX sia dal typesetting finale.} 
}

@@

\item Page 19. I think it would be interesting to give a bit more details about the conic constraints and relate it with the issue of what is a convex
constraint I discuss in point 2. I think the argument is that problems with
non-convex quadratic constraints (i.e. $f (x) \le 0$ with $f$ non-convex) may
have a convex feasible region. I imagine that detecting this in general may
be NP-hard even though the conic case (1 negative eigenvalue) is relatively
easy (e.g. if the problem includes an inequality of the form $a \cdot x \ge$ where
a is the eigenvector associated to the negative eigenvalue). It would then
be interesting to mark the problems with non-convex constraints, but for
which it is known how to show the convexity of the complete feasible
region (because they are conic or another ad-hoc reason).

\rep{TODO: Leo
% \leo{sono d'accordo col referee (ovvero: massi`, facciamolo contento)} \fabio{va qui? o e' un commento al punto di sotto?}
 }

@@

\item Page 20. ``second similar instance filter''. It would be interesting to provide a reference to the similar instances that were filtered out in case
someone wants to test on them. For that matter I am not sure I saw if
the instances have a link/reference to their source.

\rep{TODO:FABIO and Emiliano.}

\item Page 36. I am not sure if the reasoning for the name of the instances was mentioned. Is the non-consecutive order because of the filtering? (e.g.
was there a ``0017'' instance that was excluded?)

\rep{TODO:FABIO and Emiliano.
%\leo{ basta dargli una risposta secondo me} 
}

@@

\rep{[\dots] }

{\it
\begin{enumerate}

\item There are two classes of important missing application domains of QPs in Table 1: (1) trust-region subproblems, and (2) PDE-constrained optimization problems. In fact, there exist a number of PDE-constrained instances in CUTEr, which would be useful additions to the library. The authors should add at least a few such examples. the lack of these problems is worrying, because
it (implicitly) assumes that direct solvers are used, which means that this library is less relevant for matrix-free solvers.

\rep{
TODO:Fabio and Emiliano. 
%\leo{sono d'accordo, dovremmo aggiungere delle istanze da trust-region subproblem e delle istanze da problemi PDE-constrained. Chiediamo a Gould per le istanze trust-region e a Gould, Mittelmann e Sahinidis per PDE-constrained. Specifichiamo che vorremmo istanze NON gia` in CUTE.} 
}

@@

\item The taxonomy in Section 2.2.1 seems to be unaware of the fact that an indefinite Hessian does not mean that a problem is difficult. For example, saddle-point problems such as

$$ \begin{bmatrix}
G & A^T\\
A & 0
\end{bmatrix}
\begin{pmatrix}
x \\
z 
\end{pmatrix}
=
\begin{pmatrix}
-g \\
b 
\end{pmatrix}
$$

can be solved to global optimality as long as the matrix is second-order sufficient. This means
that even some QPs with indefinite Hessians can easily be solved to global optimality.

\rep{TODO:Antonio. 
%\leo{cosa vuol dire? Questa condizione si puo` testare in polytime? Sicuramente puo` entrare nel discorso a risposta dei punti 2-4 del referee \#1.} 
}

@@

\item The discussion on p.9 recounts some textbook facts, and is largely superfluous. Delete it.

\rep{TODO: Antonio.
%\leo{cancelliamo tutto!} 
%As requested, aliminated the discussion from the manuscript
}

\item What do you mean by ``exact solution of the instances'' (p.10, l.-18)? I don't believe we can even
solve $Ax = b$ ``exactly'', except in some special cases. Please clarify this statement.

\rep{TODO: Leo. 
%\leo{possiamo inserire qualche nota sui modelli di computazione per i numeri reali, razionali e floating point: (a) real numbers con real RAM model, in pratica tutti i calcoli tra numeri reali sono O(1) (la gran parte del lavoro fatto da Blum, Shub e Smale e` sulla definizione di calcolabilita` e complessita` in questo 'ambiente'); 
%(b) hic sunt leones, non si sa nemmeno se la existential theory of rationals (cioe` risolvere sistemi polinomiali su $\mathbb{Q}$) sia decidibile o no [Pheidas 2000]; 
%(c) quello che la gente fa davvero: approssimare optimality e feasibility a $\epsilon>=0$ dato, nel migliore dei casi si dimostra anche che il tempo di calcolo o numero di iterazioni e` $O(1/poly(\epsilon)) o O(log(1/\epsilon))$.
%} 
}

@@

\item The description of NLP solvers in Section 2.3.2 is at somewhat misleading. For example, KNI-
TRO is also a primal-dual interior-point method, not just a barrier code (in fact primal-dual
methods are preferred). The description of the “active-set” methods is wrong, unless you refer
to the inner method, namely the active-set QP solves. Otherwise, SNOPT and KNITRO are
SQP methods, while CONOPT is a gradient-projection method, and MINOS is an augmented
Lagrangian method. You must correct this section

\rep{TODO: Stefan and Ambros
%\leo{correggiamo gli errori e ringraziamo il referee} 
}

@@

\item Some classes of problems in Table 4 do not seem to have many instances. Please create more.

\rep{
TODO: Stefan and Ambros.
%\leo{stesso commento dell'AE -- dobbiamo mettere piu` istanze} 
}

@@

\item The y-axis labels are missing on most figures.

\rep{
TODO: Stefan and Ambros
%\leo{mettiamo la label al y axis  (duh)} 
}

@@

\item Reword the sentence ``percentage of ``hard'' eigenvalues'', p.23, l.-6. The notion of hard has a
special meaning in trust-region problems. Also, this is not a measure of hardness, as explained
above. Instead, you should consider the number of negative eigenvalues of the reduced Hessian
(wrt equality constraints). Fig. 4 is meaningless, unless you replace the definition of hardness.

\rep{
TODO: Stefan and Ambros.
% \leo{non so nulla di "hard eigenvalues" nel senso del trust region; chiediamo agli esperti} 
 }

@@

\item Improve Fig.5: (1) What do the colors mean? (2) The plot on the right is not a sparsity pattern
of any Hessian, but at best the upper triangular sparsity pattern.

\rep{TODO: Stefan and Ambros}

\item I am concerned that problems are only available in GAMS, and tested on GAMS solvers. It would make the paper stronger if the authors also released AMPL model, for example, or made use of
JuMP.

\rep{
We thank the refereee for having raised this delicate point. We definetly agree that formats are an issue.
For this reason we have translated all the instances also into the AMPL format and we have uploaded them on the website.
%\leo{Possiamo spiegare che proporre NOI le istanze in formati multipli darebbe la responsabilita` del traduttore a noi, che invece non vogliamo accettarla. D'altro canto penso che, sebbene sia stata una scelta discussa e effettuata democraticamente, non sia necessariamente la scelta giusta per ogni criterio. Per esempio, se il nostro criterio fosse la visibilita` della QPLIB (il numero di gente che la cita), dovremmo ASSOLUTAMENTE tradurre le istanze nel maggior numero possibile di formati. E se qualcuno ci fara` una correzione in futuro chi se ne frega, ringrazieremo e correggeremo. Francamente, se io fossi il dittatore della QPLIB, sceglierei di tradurre le istanze in quanti piu` formati sia possibile (almeno AMPL e SIF), e poi distribuirle con un warning.} \fabio{Adesso abbiamo anche aggiunto il formato AMPL, secondo me con questo il referee si mette tranquillo!} 
}

### 2018-01-24 AnswerToTheReferees.tex

\rep{[\dots] }

{\it
Minor Comments:
\begin{enumerate}

\item I think it would be interesting to mention the Conic library CBLIB \url{http://cblib.zib.de} and its relation to the library described in the manuscript.

\rep{We updated the manuscript by adding the suggest link to the Conic library.}

@@

\item Page 19. I think it would be interesting to give a bit more details about the conic constraints and relate it with the issue of what is a convex
constraint I discuss in point 2. I think the argument is that problems with
non-convex quadratic constraints (i.e. $f (x) \le 0$ with $f$ non-convex) may
have a convex feasible region. I imagine that detecting this in general may
be NP-hard even though the conic case (1 negative eigenvalue) is relatively
easy (e.g. if the problem includes an inequality of the form $a \cdot x \ge$ where
a is the eigenvector associated to the negative eigenvalue). It would then
be interesting to mark the problems with non-convex constraints, but for
which it is known how to show the convexity of the complete feasible
region (because they are conic or another ad-hoc reason).

\rep{TODO: Leo
% \leo{sono d'accordo col referee (ovvero: massi`, facciamolo contento)} \fabio{va qui? o e' un commento al punto di sotto?}
 }

\item Page 20. ``second similar instance filter''. It would be interesting to provide a reference to the similar instances that were filtered out in case
someone wants to test on them. For that matter I am not sure I saw if
the instances have a link/reference to their source.

\rep{The beta version of the library, which containt some of the filtered instances is available online at  \url{http://www.lamsade.dauphine.fr/QPlib2014}. We added this link to the qplib webpage.}

@@

\item Page 36. I am not sure if the reasoning for the name of the instances was mentioned. Is the non-consecutive order because of the filtering? (e.g.
was there a ``0017'' instance that was excluded?)

\rep{Yes. The numbering is due to the filtering. We added a comment on this point in the Appendix of the paper.}

### 2018-01-29 QPLIB-3.tex
Update QPLIB-3.tex
update tables 4 and 5 regarding new instances

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others.

@@

During the development of the library, a discussion ensued about
the expected goals that we wished to achieve. The following four goals
where finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       We then filtered according to a first
       measure of computational difficulty, i.e., we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       We carefully analysed the instances one by one, and we clustered them
       according to their features; for each cluster we kept only a few
       representatives (e.g., very similar size, same donor,\ldots). Finally, in order to only
       keep computationally challenging instances we ran a a complete solver for QGQ with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $251$ discrete instances and
$116$ continuous instances.

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  2 \\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   12\\[1.2 ex]
\multirow{1}*{Concave (if max)}
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
%\cmidrule(lr){2-4}
%          & \multirow{1}*{Integer}
%                    & Linear    &   1\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   11\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
\cmidrule(lr){2-4}
          & Integer & Linear    &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   13\\[1.2 ex]
                         & Quadratic &   48\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{1}*{Convex (if min)}
                         & Box       &   3 \\[1.2 ex]
\multirow{1}*{or}
                         & Linear    &   11\\[1.2 ex]
                        % & Convex    &    2\\[1.2 ex]
\multirow{1}*{Concave (if max)}
                         & Quadratic &    6\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{3}*{Quadratic}
                         & Linear    &   6\\[1.2 ex]
                         & Convex    &   1\\[1.2 ex]
                         & Quadratic &   28\\[1.2 ex]
\hline
Total                    &           & 116 \\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of continuous instances}
\label{tab:CC}
\end{table}

>>>>

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB 2010 (http://miplib.zib.de/), to mention just a few.}

@@

During the development of the library, a discussion ensued about
the expected goals that we wished to achieve. The following four goals
where finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       We then filtered according to a first
       measure of computational difficulty, i.e., we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       We carefully analysed the instances one by one, and we clustered them
       according to their features; for each cluster we kept only a few
       representatives (e.g., very similar size, same donor,\ldots). Finally, in order to only
       keep computationally challenging instances we ran a a complete solver for QGQ with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $251$ discrete instances and
$116$ continuous instances.\todo{needs update due to newly added instances ($\to$ 319 discrete 134 cont.)}

@@

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   \textcolor{red}{15}\\[1.2 ex]
          &         & Quadratic &  \textcolor{red}{151}\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  \textcolor{red}{4} \\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   12\\[1.2 ex]
\multirow{1}*{Concave (if max)}
          &         & Quadratic &    \textcolor{red}{6}\\[1.2 ex]
%          & General & Linear    &    \\
%\cmidrule(lr){2-4}
%          & \multirow{1}*{Integer}
%                    & Linear    &   1\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]
          &         & Linear    &  \textcolor{red}{74}\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   11\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
\cmidrule(lr){2-4}
          & Integer & Linear    &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & \textcolor{red}{319}\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   13\\[1.2 ex]
                         & Quadratic &   \textcolor{red}{52}\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{1}*{Convex (if min)}
                         & Box       &   3 \\[1.2 ex]
\multirow{1}*{or}
                         & Linear    &   \textcolor{red}{16}\\[1.2 ex]
                        % & Convex    &    2\\[1.2 ex]
\multirow{1}*{Concave (if max)}
                         & Quadratic &    \textcolor{red}{11}\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{3}*{Quadratic}
                         & Linear    &   6\\[1.2 ex]
                         & Convex    &   \textcolor{red}{3}\\[1.2 ex]
                         & Quadratic &   \textcolor{red}{30}\\[1.2 ex]
\hline
Total                    &           & \textcolor{red}{134} \\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of continuous instances}
\label{tab:CC}
\end{table}
